### 2023-08-05 reports/paper/resources/intervention-density-witnin-combos-a.tex
New intervention

% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:02:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[fill=fillColor] (168.95,143.84) rectangle (244.lor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (155.18,142.55) rectangle (244.94,168.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (155.18,161.56) {Distribution:\ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (155.18,150.55) rectangle (163.18,158.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] (155.18,150.55) rectangle (163.18,158.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (155.18,142.55) rectangle (163.18,150.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] (155.68,143.05) rectangle (162.68,150.05);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (165.18,151.79) {Post-intervention\ \ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (165.18,143.79) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (155.18,123.02) rectangle (231.18,140.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (155.18,134.03) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (155.18,123.02) rectangle (163.18,131.02);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (159.18,123.02) -- (159.18,131.02);
\end{scope}
\end{tikzpicture}

\end{document}
}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2023-08-04 14:49:59
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[fill=fillColor] (168.95,143.84) rectangle (244.95,163.87);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,157.35) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,146.34) rectangle (176.95,154.34);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (172.95,146.34) -- (172.95,154.34);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,147.59) {0.25 mg/m$^3$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,113.81) rectangle (240.85,141.84);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,135.32) {Distribution:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,116.31) rectangle (176.95,124.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] (169.45,116.81) rectangle (176.45,123.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,125.55) {Post-intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,117.55) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

### 2023-08-05 reports/paper/resources/intervention-density-witnin-combos-c.tex
New intervention

% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:10:09
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[fill=fillColor] (179.07, 37.60) rectangle (186.37, 46.98);

\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 46.98);

@@

\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 46.98);

\path[fill=fillColor] (222.86, 37.60) rectangle (230.16,159.58);

@@

\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 46.98);

\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 46.98);

@@

\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 46.98);

\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16,159.58);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 72.38) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,109.91) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,147.44) {30};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 75.13) --
	( 38.22, 75.13);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,112.66) --
	( 38.22,112.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,150.19) --
	( 38.22,150.19);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2023-08-04 14:50:47
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[fill=fillColor] (179.07, 37.60) rectangle (186.37,159.58);

\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 37.60);

@@

\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 37.60);

\path[fill=fillColor] (222.86, 37.60) rectangle (230.16, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 45.22);

\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 45.22);

@@

\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 45.22);

\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16,136.71);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 65.34) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 95.83) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,126.33) {30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,156.82) {40};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 68.10) --
	( 38.22, 68.10);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 98.59) --
	( 38.22, 98.59);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,129.08) --
	( 38.22,129.08);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,159.58) --
	( 38.22,159.58);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}
